R Notebook

### 2019-06-17 ICS_Cleaning.Rmd
sums over boolean phenotype data to create double positives

>>>>

```{r create new combo variables from exported boolean phenotype}
CD4<-mutate(CD4,
      #These all follow the same format
       #IFNg is the new variable. it gets assign the row sum of all the columns that have a G in the name
       TbetCXCR3=  rowSums(CD4[,grep("t_._3_.", names(CD4))]),
       TbetCCR4=  rowSums(CD4[,grep("t_._._4", names(CD4))]),
       GATA3CXCR3=  rowSums(CD4[,grep("._g_3_.", names(CD4))]),
       GATA3CCR4=  rowSums(CD4[,grep("._g_._4", names(CD4))])
)

CD4_phenotype<-mutate(CD4_phenotype,
      #These all follow the same format
       #IFNg is the new variable. it gets assign the row sum of all the columns that have a G in the name
       TH1_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH1_t_._3_.", names(CD4_phenotype))]),
       TH1_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH1_t_._._4", names(CD4_phenotype))]),
       TH1_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH1_._g_3_.", names(CD4_phenotype))]),
       TH1_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH1_._g_._4", names(CD4_phenotype))]),
      TH2_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH2_t_._3_.", names(CD4_phenotype))]),
      TH2_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH2_t_._._4", names(CD4_phenotype))]),
      TH2_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH2_._g_3_.", names(CD4_phenotype))]),
      TH2_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH2_._g_._4", names(CD4_phenotype))])
)
